Hydras \& Co.

### 2024-02-02 doc/epsilon0-chapter.tex
minor changes in pdf doc

Unfortunately, it won't work. Let us consider some well-formed term
 $\alpha=\texttt{cons $\beta\;n\;\gamma$}$, and assume that \(\beta\) and \(\gamma\) are \texttt{LT}-accessible.
In order to prove the accessibility of $\alpha$, we have to consider
any well formed term \(\delta\) such that \(\delta<\alpha\). 
But nothing guarantees that \(\delta\)  is strictly  less than \(\beta\) nor \(\gamma\), and we cannot use the induction hypotheses on   \(\beta\) nor \(\gamma\).

@@

The lemma \texttt{betaAcc} allows us to prove by well-founded induction on $\beta$, 
and natural induction on $n$ that (\texttt{cons $\alpha$ $n$ $\beta$}) is accessible.

@@

>>>>

Unfortunately, it won't work. Let us consider some well-formed term
 $\alpha=\texttt{cons $\beta\;n\;\gamma$}$, and assume that \(\beta\) and \(\gamma\) are \texttt{LT}-accessible.
In order to prove the accessibility of $\alpha$, we have to consider
any well formed term \(\delta\) such that \(\delta<\alpha\). 
% But nothing guarantees that \(\delta\)  is strictly  less than \(\beta\) nor \(\gamma\), and we cannot use the induction hypotheses on   \(\beta\) nor \(\gamma\).

@@

The new hypothesis  \texttt{beta\_Acc} allows us to prove by well-founded induction on $\beta$, 
and natural induction on $n$ that (\texttt{cons $\alpha$ $n$ $\beta$}) is accessible.

@@

\subsection{Transfinite induction}
\index{maths}{Transfinite induction}
